---
title: "P8105 HW 6"
author: "Yuki Low (yl5503)"
date: "11/27/2023"
output: github_document
---

```{r}
library(dplyr)
library(broom)
library(ggplot2)
library(modelr)
library(tidyr)
library(purrr)
library(broom)
```

Importing the weather dataframe
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

We set the seed to maintain consistency and start bootstrapping 5000 samples. We want the estimate for the intercept and both of our variables `tmin` and `prcp`. We also want the r-squared value that is calculated from each model obtained. 

```{r, warning = FALSE}
set.seed(123)

bootstrap =
  weather_df %>%
  bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df)),
    results = map(models, tidy),
    rsquared = map(models,glance)) %>%
  select(results, rsquared) %>% unnest(rsquared) %>%
  select(results, r.squared) %>% unnest(results) %>%
  select(term, estimate, r.squared) 

bootstrap
```

Plotting the distribution of $R^2$
```{r}
bootstrap %>%
  filter(term == "(Intercept)") %>%
  ggplot(aes(x = r.squared)) +
  geom_density()
```
From looking at the distribution of R-squared values, it can be seen that there is a slight left skew. 

Calculating the confidence interval for R-squared value. 
```{r}
r_squared_CI <-
  bootstrap %>%
  filter(term == "(Intercept)") %>%
  select(r.squared) %>%
  summarize(ci_lower = quantile(r.squared, 0.025), 
            ci_upper = quantile(r.squared, 0.975))

r_squared_CI
```
We are 95% confident that our true r-squared value falls in between the interval (`r r_squared_CI[1]`, `r r_squared_CI[2]`)

Distribution of $log(\beta_1 * \beta_2)$
```{r}
bootstrap %>%
  pivot_wider(names_from = term, values_from = estimate) %>% 
  rename(beta_1 = tmin, 
         beta_2 = prcp) %>% 
  mutate(log_beta1_beta2 = log(beta_1 * beta_2)) %>% 
  ggplot(aes(x = log_beta1_beta2)) + 
  geom_density()
```
The distribution of our $log(\beta_1 * \beta_2)$ terms is skewed to the left. 


```{r}
log_beta1_beta2_CI <- bootstrap %>%
  pivot_wider(names_from = term, values_from = estimate) %>% 
  rename(beta_1 = tmin, 
         beta_2 = prcp) %>% 
  mutate(log_b1_b2 = log(beta_1 * beta_2)) %>%
  summarize(ci_lower = quantile(log_b1_b2, 0.025, na.rm = T), 
            ci_upper = quantile(log_b1_b2, 0.975, na.rm = T), 
            NA_count = sum(is.na(log_b1_b2)))
            
log_beta1_beta2_CI
```

We are 95% confident that our true $log(\beta_1 * \beta_2)$ value falls in between the interval (`r log_beta1_beta2_CI[1]`, `r log_beta1_beta2_CI[2]`)